Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\contained_{R_{k-2}}(\bm{t}) = \contained_{R_{k-2}}(h^*)$. We can then derive that
\myeqn{
    \sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)| 
    &\le& \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\contained_{R_{k-2}}(\bm{t})| \nn \\
    &\leq& \out, \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

>>>>

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\contained_{R_{k-2}}(\bm{t}) = \contained_{R_{k-2}}(h^*)$. We can then derive 
\myeqn{
    && \sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)|  \nn \\ 
    &\le& \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\contained_{R_{k-2}}(\bm{t})| 
    \leq \out \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.
